A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-17 doc/large_strain.tex
Add IWR processor information

In this section we apply the proposed matrix-free operator algorithms for finite-strain hyper-elastic material as well as the geometric multigrid preconditioner to a benchmark problem from \cite{Miehe2007}. Coarse mesh for 2D and 3D problems is depicted in Figure \ref{fig:miehe}. The 2D material consists of a matrix (depicted in blue), a hole and two spherical inclusions (depicted in red). The size of the square domain is $10^{-3} \rm{mm}$.
The matrix material is taken to have Poisson's ratio of $0.3$ and shear modulus $\mu=0.4225 \times 10^6\, \rm{N/mm^2}$. The inclusion is take to be $100$ times harder.
The 3D material is obtained by extrusion in the third direction.
Note that a relatively coarse mesh is adopted at the coarsest multigrid level, however the geometry of inclusions is captured accurately by employing manifold description of the boundaries and interfaces.
Both domains are fixed at the bottom surface and the distributed load is applied at the top in $(1,0)$ and $(1,1,0)$ direction for 2D and 3D problems, respectively.
The load of $0.5\,\rm{N}$ is applied in 5 steps. The displacement tolerance for Newton update is taken to be $10^{-5}$ whereas the relative and absolute tolerances for forces $10^{-8}$. The relative convergence criteria for linear solver is $10^{-6}$.
%
Figure \ref{fig:miehe_gmg} illustrates the multigrid mesh for the 2D problem after two global refinements.
%
The benchmark calculations are performed for 2D and 3D problems with various combination of polynomial degrees and number of global refinements, see Tables \ref{tab:input_parameters_2d} and \ref{tab:input_parameters_3d}.
%
We are interested in the following metrics:
(i) walltime per DoF of matrix-vector multiplication;
(ii) memory requirement per DoF;
(iii) average number of CG iterations throughout the whole run (i.e. each Newton-Raphson iteration and each loading step);
(iv) walltime per DoF of CG solver;
%
The results of the matrix-free approach with geometric-multigrid preconditioner are compared to the matrix-based approach with algebraic multigrid (AMG) preconditioner using Trilinos \cite{Heroux2005} library.
The aggregation threshold for AMG is taken as $10^{-4}$.
Computations are done on a single node of two clusters.
A node on ``Emmy'' cluster has two Xeon 2660v2 ``Ivy Bridge'' chips (10 cores per chip + SMT) running at 2.2 GHz with 25 MB Shared Cache per chip and 64 GB of RAM. Intel compilers version 18.03 with flags ``-O3 -march=native'' and Intel MPI version 18.03 are used.
A node on ``IWR'' cluster
{\color{red}Daniel please add...}

>>>>

In this section we apply the proposed matrix-free operator algorithms for finite-strain hyper-elastic material as well as the geometric multigrid preconditioner to a benchmark problem from \cite{Miehe2007}. Coarse mesh for 2D and 3D problems is depicted in Figure \ref{fig:miehe}. The 2D material consists of a matrix (depicted in blue), a hole and two spherical inclusions (depicted in red). The size of the square domain is $10^{-3} \rm{mm}$.
The matrix material is taken to have Poisson's ratio of $0.3$ and shear modulus $\mu=0.4225 \times 10^6\, \rm{N/mm^2}$. The inclusion is take to be $100$ times harder.
The 3D material is obtained by extrusion in the third direction.
Note that a relatively coarse mesh is adopted at the coarsest multigrid level, however the geometry of inclusions is captured accurately by employing manifold description of the boundaries and interfaces.
Both domains are fixed at the bottom surface and the distributed load is applied at the top in $(1,0)$ and $(1,1,0)$ direction for 2D and 3D problems, respectively.
The load of $0.5\,\rm{N}$ is applied in 5 steps. The displacement tolerance for Newton update is taken to be $10^{-5}$ whereas the relative and absolute tolerances for forces $10^{-8}$. The relative convergence criteria for linear solver is $10^{-6}$.
%
Figure \ref{fig:miehe_gmg} illustrates the multigrid mesh for the 2D problem after two global refinements.
%
The benchmark calculations are performed for 2D and 3D problems with various combination of polynomial degrees and number of global refinements, see Tables \ref{tab:input_parameters_2d} and \ref{tab:input_parameters_3d}.
%
We are interested in the following metrics:
(i) walltime per DoF of matrix-vector multiplication;
(ii) memory requirement per DoF;
(iii) average number of CG iterations throughout the whole run (i.e. each Newton-Raphson iteration and each loading step);
(iv) walltime per DoF of CG solver;
%
The results of the matrix-free approach with geometric-multigrid preconditioner are compared to the matrix-based approach with algebraic multigrid (AMG) preconditioner using Trilinos \cite{Heroux2005} library.
The aggregation threshold for AMG is taken as $10^{-4}$.
Computations are done on a single node of two clusters.
A node on ``Emmy'' cluster has two Xeon 2660v2 ``Ivy Bridge'' chips (10 cores per chip + SMT) running at 2.2 GHz with 25 MB Shared Cache per chip and 64 GB of RAM. Intel compilers version 18.03 with flags ``-O3 -march=native'' and Intel MPI version 18.03 are used.
The ``IWR'' results were obtained ona single machine with eight Xeon E7-8870 ``Sandy Bridge'' chips (10 cores per chip  + SMT) running at 2.4 GHz with 30 MB Shared Cache per chip. For the simulation, GNU 8.1.0 with flags ``-O3 -march=native'' and OpenMPI 3.0.0 were used.
